Pilot study Aperol: questionnaire data

### 2021-01-13 studies/2020_Aperol_Git/questionnaire data/questionnaire_data_mandy.Rmd
update questionnaire R scrpit & excel

# load tab delimited text file into R; 
# file should be in a subfolder named "data" for the script to select it
raw.data<-read.table("./data/questionnaire_data_080121.txt",sep="\t", header=T)

@@

# # change data structure: everything is turned into factors except for 
# main.data <- raw.data %>%
#   filter(what == "data"& valid == 1)  %>%
#   mutate(across(!correct&!agem&!aged, as.factor),
#          correct = as.integer(correct))

>>>>

# load tab delimited text file into R; 
# file should be in a subfolder named "data" for the script to select it
raw.data<-read.table("./data/short_questionnaire_data_1301211.txt",sep="\t", header=T)

@@

### checking for missing values
apply(is.na(raw.data), 2, which)

# knock out NAs
raw.data <- raw.data  %>% filter(
  personID != "NA")

view (raw.data)
str(raw.data)

### Data collection
For the pilot study, we collected data from . The table shows the state of data collection as of `r Sys.Date()`.

```{r overview demographics data table, echo=FALSE}
raw.data %>% # select data
  group_by(session, target, perspective) %>%
  summarise(N = n_distinct(personID),
            male = sum(sex),
            "mean age" = round(mean(age), 2),
            "min age" = min(age),
            "max age" = max(age),
            "sd age" = round(sd(age), 2),
            ) %>% 
  knitr::kable(digits = 2)
